\chapter{Fields}

\begin{remark}
    We begin by recalling the definition of a field.
    Fields are quintuples \((F,+,\cdot,0,1)\) where
    \((F,+,0)\) and \((F^\star,\cdot,1)\) are both abelian groups,
    and multiplication distributes over addition.
\end{remark}
\begin{remark}
    Fields are commutative rings,
    so theorems in Chapter~\ref{sec:rings} will entirely hold,
    and we will be using those theorems throughout.
\end{remark}
\begin{remark}
    Much of our foundation will come from extending any integral domain \(R\)
    (in particular \(\bZ\))
    to its field of fractions \(F\) (in particular \(\bQ\)).
\end{remark}


\section{Field Extensions}

\begin{definition}
    Suppose \(F\) is a field, and \(F[x]\) its polynomial ring.
    Corollary~\ref{cor:field-polynomial-pid} tells us that
    \(F[x]\) is a domain,
    and hence we can construct its field of fractions,
    which we denote \(F(X) = \{\frac{f(x)}{g(x)} : f,g \in F[x], g \neq 0\}\).
    This is often called the transcendental extension of \(F\),
    or the univariate function field over \(F\).
\end{definition}

\begin{remark}
    Recall that if \(R\) is a commutative ring,
    \(P\) a prime ideal, and \(M\) a maximal ideal,
    then \(R/P\) \hyperref[prop:prime-quotient-domain]{is an integral domain}
    and \(R/M\) \hyperref[cor:maximal-quotient-field]{is a field}.
    But when \(F\) a field,
    \hyperref[prop:pid-maximal-is-prime]{prime ideals and maximal ideals are the same thing}.
\end{remark}

\begin{definition}
    Suppose \(F\) is a field.
    A field extension \(K/F\) is a field \(K \supseteq F\).
    We say \(F\) is a subfield of \(K\),
    where \(F\) is a base field, and \(K\) is an over field of \(F\).

    In commutative diagrams, we often denote this as
    \begin{center}
        \begin{tikzcd}
            K \arrow[dash]{d} \\ F
        \end{tikzcd}
    \end{center}
\end{definition}

\begin{proposition}\label{prop:field-extension-vsp}
    Suppose \(K/F\) a field extension.
    \(K\) can be characterized as a vector space over \(F\).
\end{proposition}
\begin{proof}
    Let \(k,\ell \in K\), and \(\lambda \in F\).
    Trivially by field addition \(k + \ell \in K\),
    and \(\lambda \in F \subseteq K\),
    so by field multiplication we have \(\lambda k \in K\).
    Moreover, distributivity holds because of
    \(\lambda(k+\ell) = \lambda k + \lambda \ell\)
    due to distributivity in \(K\).
\end{proof}

\begin{definition}
    Suppose \(K/F\) field extension.
    We call \(K/F\) finite or \(K\) is a finite extension of \(F\)
    if \(K\) is a finite-dimensional vector space over \(F\).
    If \(K/F\) finite, the degree of \(K/F\),
    denoted \([K:F] = \dim_F K\)
    is the dimension of \(K\) as an \(F\)-space.
\end{definition}
\begin{theorem}\label{thm:finite-extension-stack}
    Suppose \(K/F\) and \(L/K\) are finite field extensions.
    Then \(L/F\) is a finite extension,
    and in particular, \([L:F] = [L:K][K:F]\).
\end{theorem}
\begin{proof}
    Since \(K/F\) finite, let \({\{a_i\}}_{i=1}^m\) be a basis for \(K/F\),
    so \([K:F] = m\).
    For every \(a \in K\), we can write \(a = \sum_{i=1}^m \lambda_i a_i\)
    for some \(\lambda_i \in F\).
    Similarly since \(L/K\) finite,
    let \({\{b_j\}}_{j=1}^n\) be a basis for \(L/K\), so \([L:K] = n\).
    For every \(b \in L\), we can write \(b = \sum_{j=1}^n \mu_j b_j\)
    for some \(\mu_j \in K\).
    But then we have a linear combination of \(mn\) elements
    \begin{equation*}
        b = \sum_{j=1}^n \mu_j b_j
        = \sum_{j=1}^n \qty(\sum_{i=1}^m \lambda_{ij} a_i) b_j
        = \sum_{i,j=1}^{m,n} \lambda_{ij} (a_i b_j)
    \end{equation*}
    It suffices to check that \({{\{a_i b_j\}}_{i=1}^m}_{j=1}^n\) forms a basis.
    Suppose that
    \begin{equation*}
        0 = \sum_{i,j=1}^{m,n} \lambda_{ij} (a_i b_j)
        = \sum_{j=1}^n \qty(\sum_{i=1}^m \lambda_{ij} a_i) b_j
    \end{equation*}
    But by linear independence of \(b_j\),
    for each individual \(j\), \(\sum_{i=1}^m \lambda_{ij} a_i = 0\),
    and by linear independence of \(a_i\),
    for all \(i\), \(\lambda_{ij} = 0\).
    This proves linear independence.
\end{proof}
\begin{corollary}
    Finiteness is a property that is stackable,
    and degree of extension is multiplicative.
\end{corollary}
\begin{proof}
    Merely proceed by induction on the tower of field extensions,
    applying the \hyperref[thm:finite-extension-stack]{theorem above}.
\end{proof}

\begin{theorem}\label{thm:field-hom-injective}
    Every field homomorphism is injective.
\end{theorem}
\begin{proof}
    Suppose \(\func{\phi}{F}{K}\) is a field homomorphism.
    By way of contradiction, suppose \(\phi\) is not injective.
    Then there exists \(a,b \in F\) such that \(\phi(a) = \phi(b)\) and \(a \neq b\).
    But that tells us \(f(a-b) = 0 = f(0)\), and in particular,
    since \(a-b \neq 0\), \(f(a-b)f({(a-b)}^{-1}) = f(1) = 1\).
    But that implies \(0f({(a-b)}^{-1}) = 1\) which is a contradiction.
\end{proof}


\section{Algebraic Extensions}

\begin{definition}
    Suppose \(K/F\) is a field extension, and \(a \in K\) some element.
    We call \(a\) algebraic over \(F\)
    if there exists a (monic) polynomial \(f(x) \in F[x]\) such that \(f(a) = 0\).
    If \(a \in K\) is not algebraic over \(F\),
    we call \(a\) transcendental over \(F\).
\end{definition}

\begin{definition}
    Suppose \(a \in K\) is algebraic over \(F\).
    The minimal polynomial of \(a\) over \(F\),
    either denoted \(\min_F(a)\) or \(\min(a;F)\)
    is the irreducible polynomial \(f(x) \in F[x]\)
    with the lowest degree such that \(f(a) = 0\).
\end{definition}
\begin{proposition}
    A monic minimal polynomial exists and is unique for every algebraic \(a \in K\).
\end{proposition}
\begin{proof}
    By definition there must be some polynomial that it satisfies.
    If it is reducible, reduce it into irreducible components,
    and \(a\) must satisfy one of those irreducible components.
    It is unique since if another monic polynomial \(g(x)\) satisfies our conditions,
    \((g-f)(x)\) also satisfies our conditions,
    and since they are the same degree, \(\deg(g-f) < \deg f\) violates minimality.
\end{proof}
\begin{definition}
    Suppose \(a \in K\) is algebraic over \(F\).
    We define the degree of \(a\) to be the degree of its minimal polynomial,
    \(\deg a = \deg \min_F(a)\).
\end{definition}

\begin{definition}
    Suppose \(K/F\) is a field extension.
    If all elements \(a \in K\) are algebraic over \(F\),
    we call \(K/F\) an algebraic extension.
\end{definition}
\begin{definition}
    Suppose \(K/F\) is an extension, and \(a \in K\) some element.
    \(F(a) \subseteq K\) is the smallest subfield that contains \(F\)
    and all elements \(\lambda = \sum_i \ell_i a^i\) for some \(\ell_i \in F\).
\end{definition}
\begin{proposition}
    \(F(a)\) is the field of fractions of \(F[a]\).
\end{proposition}
\begin{proof}
    By definition of a field of fractions,
    \(F(a)\) is the smallest field that contains \(F[a]\).
\end{proof}
\begin{theorem}\label{thm:algebraic-finite-extension}
    Suppose \(K/F\) is a field extension, and \(a \in K\) some element.
    The following are equivalent:
    \begin{enumerate}[label={(\alph*)}, itemsep=0mm]
        \item \(a\) is algebraic over \(F\);
        \item \(F(a)\) is a finite extension of \(F\); and
        \item \(F[a] = F(a)\).
    \end{enumerate}
\end{theorem}
\begin{proof}
    We first prove that (a) implies (c).
    Since \(a\) is algebraic, there is some minimal polynomial
    \(a^n + \lambda_1 a^{n-1} + \cdots + \lambda_n = 0\) for \(\lambda_i \in F\).
    But we can rewrite the above as
    \begin{equation*}
        -\lambda_n = a^n + \lambda_1 a^{n-1} + \cdots + \lambda_{n-1}a
        = a(a^{n-1} + \lambda_1 a^{n-2} + \cdots + \lambda_{n-1})
    \end{equation*}
    and clearly \(\lambda_n \neq 0\),
    since otherwise \(a^{n-1} + \lambda_1 a^{n-2} + \cdots + \lambda_{n-1}\)
    would be a minimal polynomial of degree less than \(n\),
    violating minimality of the original polynomial.
    Hence we have a polynomial expression for the inverse
    \begin{equation*}
        a^{-1} = -\frac{1}{\lambda_n}
        (a^{n-1} + \lambda_1 a^{n-2} + \cdots + \lambda_{n-1})
    \end{equation*}
    so \(F(a) \subseteq F[a]\).
    \(F[a] \subseteq F(a)\) by definition
    and we have equality.
    
    We now prove that (c) implies (b).
    For any \(i \geq 0\), \(a^{n+i}\) is in the \(F\)-span of \({\{a^j\}}_{j=0}^{n-1}\).
    and since we write elements in \(F(a) = F[a]\)
    as linear combinations of powers of \(a\),
    the degree of those elements must be at most \(n\),
    hence \([F(a):F]\) is finite.

    Lastly we prove that (b) implies (a).
    Suppose \(F(a)\) is a finite extension.
    Then \({\{a^i\}}_{i=0}^\infty \subseteq F(a)\) is a linearly dependent set.
    We shall find the smallest \(ell\) such that
    \({\{a^i\}}_{i=0}^\ell\) is a linearly dependent set.
    By linear dependence we will have
    \(\lambda_0 + \lambda_1 a + \cdots + \lambda_\ell a^\ell = 0\)
    for some \(\lambda_i \in F\), \(\lambda_\ell \neq 0\).
    Hence we have found a degree \(\ell\) polynomial that \(a\) satisfies,
    and \(a\) must be algebraic.
\end{proof}
\begin{corollary}\label{cor:algebraic-finite-extension}
    Suppose \(K/F\) is a finite extension.
    Then \(K\) is algebraic over \(F\).
\end{corollary}
\begin{proof}
    Suppose \(a \in K\).
    Since we have \(F \subseteq F(a) \subseteq K\),
    \(F(a)/F\) must be finite,
    which by the \hyperref[thm:algebraic-finite-extension]{theorem above}
    must be algebraic.
\end{proof}
\begin{remark}
    We have shown that finite extensions are algebraic,
    but algebraic extensions are not necessarily finite.
\end{remark}

\begin{theorem}
    Suppose \(K/F\) is a field extension.
    The set of all \(F\)-algebraic elements in \(K\)
    form a subfield of \(K\) containing \(F\).
\end{theorem}
\begin{proof}
    Let \(a,b \in K\) be algebraic over \(F\).
    It is sufficient to prove that \(a \pm b\), \(ab\),
    and \(a/b\) when \(b \neq 0\) are all algebraic.
    Observe that \([F(a):F],[F(b):F]\) are finite by the
    \hyperref[thm:algebraic-finite-extension]{previous theorem}.
    Let \(F_1 = F(a) \subseteq K\).
    Then again, \([F_1(b):F]\) is also finite by Theorem~\ref{thm:finite-extension-stack}.
    This process is repeatable for finitely many elements.
    From this we can see that \(F(a)(b) = F(a,b)\)
    by minimality of the extension by an element.
    But then this tells us that \(a,b \in F(a,b)\) is a field,
    so \(a \pm b\), \(ab\), and \(a/b\) are all in \(F(a,b)\).
    and finite implies algebraic
    by the \hyperref[thm:algebraic-finite-extension]{theorem above}.
    % It is now sufficient to prove that \(\)
    % Now suppose \(S \subseteq K\) is a subset,
    % and let \(F(S)\) be the smallest subfield of \(K\) containing \(F\) and \(S\).
\end{proof}
\begin{definition}
    Suppose \(K/F\) is an extension.
    Then the subfield of all \(F\)-algebraic elements in \(K\)
    is usually denoted \(F^\text{alg} \subseteq K\).
    \(K/F^\text{alg}\) has no algebraic elements over \(F\),
    while \(F^\text{alg}/F\) is an algebraic extension.
\end{definition}

\begin{definition}
    Suppose \(K/F\) is an extension.
    \(K/F\) is finitely generated if there exists a finite set \(S \subseteq K\)
    such that \(K = F(S)\).
\end{definition}
\begin{theorem}\label{thm:finitely-gen-algebraic}
    Suppose \(K/F\) is finitely generated by \(S\).
    If all elements of \(S\) are algebraic, then \(K/F\) is algebraic.
\end{theorem}
\begin{proof}
    If \(S = {\{s_i\}}_{i=1}^n\),
    then merely apply Theorem~\ref{thm:algebraic-finite-extension}
    to see that \(F(S)/F\) is finite,
    so Corollary~\ref{cor:algebraic-finite-extension}
    tells us that it is algebraic.
\end{proof}
\begin{corollary}\label{cor:algebraic-extension-stack}
    Suppose \(K/F\) and \(L/K\) are algebraic extensions.
    Then \(L/F\) is algebraic.
\end{corollary}
\begin{proof}
    Suppose \(\lambda \in L\).
    Then there exists \(f(x) \in K[x]\) such that \(f(\lambda) = 0\).
    \(f(x) = x^n + b_1 x^{n-1} + \cdots + b_0\) where \(b_i \in K\).
    But notice that \(b_i \in K\) are algebraic over \(F\),
    so \(F(b_1,\hdots,b_n)/F \subseteq K\) is a finite extension
    by the \hyperref[thm:finitely-gen-algebraic]{theorem above}.
    We can see that \(f(x)\) is also a polynomial in \(F(b_1,\hdots,b_n)[x]\),
    which tells us that \(F(b_1,\hdots,b_n)(\lambda)/F(b_1,\hdots,b_n)\) is finite.
    But these two finite extensions combined gives us that
    \(F(b_1,\hdots,b_n)(\lambda)/F\) is finite by Theorem~\ref{thm:finite-extension-stack}.
    Since \(F(\lambda) \subseteq F(b_1,\hdots,b_n)\),
    \(F(\lambda)/F\) must also be finite,
    which implies \(\lambda\) is algebraic over \(F\)
    by Theorem~\ref{thm:algebraic-finite-extension}.
\end{proof}


\section{Splitting Fields and Algebraic Closures}

\begin{theorem}\label{thm:field-extension-gain-root}
    Suppose \(f(x) \in F[x]\) is an irreducible polynomial of degree at least 2,
    There exists an extension \(K/F\) such that \(f(x)\) has roots in \(K\).
\end{theorem}
\begin{proof}
    Let \(I = (f(x)) \subseteq F[x]\) be a maximal ideal,
    since \(f(x)\) is irreducible by Theorem~\ref{thm:ideal-divisibility}.
    Then we have a field \(K = F[x]/I \supseteq F\)
    by Corollary~\ref{cor:maximal-quotient-field},
    with degree \([K:F] = \deg f\) which we will say is \(n\).
    This induces a homomorphism \(\func{\pi\circ\iota}{F}{K}\)
    where \(\func{\iota}{F}{F[x]}\) is the inclusion of \(F\) into its polynomial ring,
    and \(\func{\pi}{F[x]}{K}\) is the quotient by \(I\),
    both of them ring homomorphisms.
    We can see that \(\pi\circ\iota\) is a field homomorphism,
    since elements in \(F\) within \(F[x]\) will not get collapsed by \(I\)
    as their degrees are always 1.
    Now see that \(\pi(f(x)) = \overline{f(x)} = 0\) in \(K\),
    so \(f(\bar{x}) = 0\), and \(\pi\) maps \(x \mapsto \bar{x}\),
    so \(\bar{x}\) is a root in \(K\),
    and \(K = \langle 1, x, \hdots, x^{n-1} \rangle\).
\end{proof}
\begin{corollary}
    If \(f(x) \in F[x]\) has degree \(n\),
    then there exists a field extension \(K/F\)
    with \([K:F] \leq n\) such that \(f(x)\) acquires a root.
\end{corollary}
\begin{proof}
    Split \(f(x)\) into irreducible components
    and then apply the \hyperref[thm:field-extension-gain-root]{theorem above}.
\end{proof}

\begin{definition}
    Suppose \(L_1/F\) and \(L_2/F\) are field extensions,
    where \(L_1,L_2 \subseteq L\).
    The composite extension or the compositum,
    denoted \(L_1 \cdot L_2\) or \(L_1 L_2\),
    is the smallest field extension of \(F\) in \(L\)
    that contains both \(L_1\) and \(L_2\).
\end{definition}

\begin{definition}
    A polynomial \(f(x) \in F[x]\) splits over an extension \(K/F\)
    if \(f(x) \in K[x]\) can be written as a product of linear polynomials,
    i.e.\ all roots exist in \(K\).
\end{definition}

\begin{definition}
    Suppose \(K/F\) is an extension.
    An automorphism of \(K\) is a field automorphism \(\sigma \in \Aut(L)\)
    that is bijective;
    an \(F\)-automorphism is a field automorphism \(\sigma \in \Aut_F(L)\),
    with the additional condition that it is the identity when restricted to \(F\),
    \(\sigma\vert_F = \id_F\).
\end{definition}
\begin{lemma}
    Suppose \(K/F\) is an extension,
    and \(\sigma \in \Aut_F(K)\) an \(F\)-automorphism.
    If \(a \in K\) is an element with a minimal polynomial \(\min_F(a) = f(x)\),
    then \(\sigma(a)\) is also a root of \(f(x)\).
\end{lemma}
\begin{proof}
    By definition \(a\) is a root of \(f(x)\), so \(f(a) = 0\).
    But \(\sigma(f(a)) = \sigma(0) = 0\),
    and notice that \(\sigma(f(x)) = f(x)\),
    since the coefficients are in \(F\) so they remain unchanged under \(\sigma\),
    so \(f(\sigma(a)) = 0\).
\end{proof}

\begin{definition}
    The splitting field of a polynomial \(f(x) \in F[X]\) over \(F\)
    is a field \(K\) such that
    \begin{enumerate}[label={(\roman*)}, itemsep=0mm]
        \item \(f(x)\) splits completely over \(K\);
        \item \(K \supseteq F\); and
        \item if \(K'\) satisfies the previous two conditions,
            then \(K' \supseteq K\).
    \end{enumerate}
\end{definition}
\begin{proposition}[Existence of Splitting Fields]\label{prop:splitting-field-existence}
    For any \(f(x) \in F[x]\), its splitting field exists.
\end{proposition}
\begin{proof}
    Without loss of generality suppose \(f(x)\) irreducible and monic.
    By Theorem~\ref{thm:field-extension-gain-root},
    we can find a field extension \(F_1/F\)
    such that \(f(x) = (x-a_1)f_1(x) \in F_1[x]\).
    Iterate on \(f_i(x)\) until \(f(x)\) is comprised of linear factors.
\end{proof}
\begin{corollary}
    Let \(f(x) \in F[x]\) be a polynomial of degree \(n\).
    Then there exists an extension \(K/F\) with degree \([K:F] \leq n!\)
    such that \(F\) splits completely over \(K\).
\end{corollary}
\begin{proof}
    Same proof as \hyperref[prop:splitting-field-existence]{proposition above},
    but notice that \([F_1:F] \leq n\),
    and then induct on \(n\), since \(\deg f_1(x) \leq n-1\).
\end{proof}

% \begin{definition}
%     Suppose \(F\) is a field.
%     An algebraic closure \(\overline{F}\) is a field that
%     every polynomial \(f(x) \in F[x]\) splits completely over \(\overline{F}\),
%     and every element is algebraic over \(F\).
% \end{definition}
\begin{lemma}
    Suppose \(F\) is a field.
    Then the following are equivalent:
    \begin{enumerate}[label={(\alph*)}, itemsep=0mm]
        \item The only algebraic extension of \(F\) is itself;
        \item The only finite extension of \(F\) is itself;
        \item If \(K/F\) is an extension,
            then \(F\) is the set of \(F\)-algebraic elements in \(K\);
        \item Every \(f(x) \in F[x]\) splits over \(F\); and
        \item Every \(f(x) \in F[x]\) has a root in \(F\).
    \end{enumerate}
\end{lemma}
\begin{proof}
    (a) implies (b) is the contrapositive of Corollary~\ref{cor:algebraic-finite-extension}.

    (b) implies (c) because if there exists another \(F\)-algebraic element \(a \in K-F\),
    then there is a finite extension \(F(a)/F\).

    (c) implies (d) since if \(f(x) \in F[x]\) and \(a\) is a root,
    then \(a\) is algebraic over \(F\), and must be in \(F\).
    Induct on order of \(f\).

    (d) implies (e) trivially true.

    (e) implies (d) simply by induction on degree of \(f\).

    (d) implies (a) since if there are other algebraic extensions,
    then that means there is some polynomial that does not have a root in \(F\).
\end{proof}
\begin{definition}
    \(F\) is algebraically closed if it satisfies any of the conditions above.
\end{definition}
% \begin{proposition}
%     Algebraic closures are algebraically closed.
% \end{proposition}
% \begin{proof}
%     It is sufficient to prove that \(\overline{\overline{F}} = \overline{F}\).
%     Suppose \(p(x) \in \overline{F}[x]\) is a polynomial
%     and let \(a\) be a root of \(p(x)\).
%     Let \(f(x) = \min_{\overline{F}}(a)\) be the minimal polynomial.
% \end{proof}

\begin{definition}
    If \(K\) is an algebraic extension of \(F\) and is algebraically closed,
    then \(K\) is an algebraic closure of \(F\).
\end{definition}
\begin{theorem}[Existence of Algebraic Closures]
    Suppose \(F\) is a field.
    Then there exists an algebraically closed field \(K \supseteq F\).
\end{theorem}
\begin{proof}
    We first attempt to construct an extension \(F_1/F\)
    such that every polynomial \(f(x) \in F[x]\) of degree at least 1
    has at least one root.
    For every \(f(x) \in F[x]\) let us assign an arbitrary letter
    (some unique indeterminate) \(X_f\),
    and let \(S\) be the set of all \(X_f\).
    We can get a bijection between \(S\) and \(F[x] - F\).
    We now get a multivariate polynomial ring \(F[S]\).

    We now wish to show that the ideal \(I\) generated by all \(f(X_f)\)
    is not the unit ideal \((1) = F[S]\).
    Suppose, by way of contradiction, that \(I = (1) = F[S]\).
    % TODO: see alg closed in 422
\end{proof}
\begin{corollary}
    Suppose \(F\) is a field,
    then there exists an algebraic extension \(F^\text{alg}/F\)
    that is algebraically closed.
\end{corollary}
\begin{proof}
    % TODO: see alg closed in 422
\end{proof}

\begin{proposition}
    Suppose \(\func{\sigma}{F}{L}\) is a field homomorphism,
    where \(L = \overline{L}\) iss algebraically closed.
    Let \(\alpha\) be algebraic over \(F\),
    \(p(x) = \min_F(a) = \sum_{i=0}^n a_i x^i\) a monic minimal polynomial,
    and \(\sigma(p)(x) = \sum_{i=0}^n \sigma(a_i)x^i\) its image.
    Then given a homomorphism \(\func{\tau}{F(\alpha)}{L}\)
    that is an extension of \(\sigma\) (\(\tau\vert_F = \sigma\)),
    the evaluation map \(\tau \mapsto \tau(\alpha)\)
    is a bijection between homomorphisms extending \(\sigma\)
    (\(\{\tau\in\Hom(F(\alpha),L): \tau\vert_F = \sigma\}\))
    and the roots of the image polynomial in \(L\)
    (\(\{\beta \in L : \sigma(p)(\beta) = 0\}\)).
\end{proposition}
\begin{proof}
    Let \(\func{\tau}{F(\alpha)}{L}\) extending \(\sigma\).
    Then \(\tau(p(\alpha)) = \sigma(p)(\tau(\alpha)) = 0\)
    since \(p(\alpha) = 0\).
    % TODO
\end{proof}

\begin{theorem}[Uniqueness of Splitting Fields]\label{thm:uniqueness-splitting-field}
    Suppose \(p(x) \in E[x]\) an irreducible polynomial,
    and \(K\) is a splitting field of \(p(x) \in E[x]\).
    Suppose \(\func{\phi}{E}{F}\) is a field isomorphism,
    and \(L\) is a splitting field of \(\phi(p)(x) \in F[x]\).
    Then \(\phi\) extends to an isomorphism \(\func{\sigma}{K}{L}\)
    where \(\sigma\vert_E = \phi\).
    In particular, splitting fields of \(p(x) \in F[x]\) over \(F\)
    are \(F\)-isomorphic.
\end{theorem}


\section{Separability}

\begin{definition}
    An (irreducible) polynomial \(f(x) \in F[x]\) of degree \(n\)
    is separable if \(f(x)\) has \(n\) distinct roots in its splitting field,
    or equivalently, if its irreducible factors are distinct and separable.
\end{definition}
\begin{proposition}\label{prop:derivative-inseparability}
    \(f(x) \in F[x]\) is inseparable
    if and only if \(f\) and \(f'\) share a root.
\end{proposition}
\begin{proof}
    Suppose \(f(x)\) is separable.
    Then we can write, in its splitting field,
    that \(f(x) = \prod_i (x-r_i)\) for all distinct \(r_i\).
    By the product rule,
    \(f'(x)\) has one term that is missing \(x-r_i\),
    and all other terms contain \(x-r_i\),
    Let us inspect \(f'(r_i)\).
    All the terms that contain \(r_i\) will evaluate to 0,
    while the term that has \(r_i\) missing will evaluate to nonzero.
    Hence \(0 = f(r_i) \neq f'(r_i)\).

    Now suppose \(f(x)\) is inseparable.
    Then there is some root \(r\) that has multiplicity \(m > 1\),
    so we write in a splitting field \(f(x) = {(x-r)}^m g(x)\).
    The formal derivative is then \(f'(x) = m{(x-r)}^{m-1} g(x) + {(x-r)}^m g'(x)\).
    Hence \(f(r) = f'(r) = 0\).
\end{proof}

\begin{definition}
    Suppose \(f(x) \in F[x]\) is a (monic) polynomial,
    and over a splitting field is written as
    \(f(x) = \prod_{i=1}^k {(x-r_i)}^{m_i}\)
    where \(r_i\) are all distinct and \(m_i \geq 1\).
    The multiplicity of a root \(r_i\) is \(m_i\).
    We call \(r_i\) a simple root if \(m_i = 1\),
    and we say \(f(x)\) has repeated roots if there exists \(i\)
    such that \(m_i > 1\).
\end{definition}

\subsection*{Resultant and Determinant}

\begin{remark}
    Historically the resultant is very important in determining separability,
    but in modern times the discriminant is more often used.
    Nevertheless, we shall include it here for sake of completeness.
\end{remark}
\begin{definition}
    Suppose \(f(x),g(x) \in F[x]\) are polynomials;
    \(f(x) = \sum_{i=0}^n a_i x^{n-i}\) and \(g(x) = \sum_{j=0}^m b_j x^{m-j}\),
    and the leading terms are nonzero.
    The resultant of \(f\) and \(g\) is
    \begin{equation*}
        \mathcal{R}(f,g) = a_0^m b_0^n \prod_{i,j} (\alpha_i - \beta_j)
    \end{equation*}
    where \(\alpha_i\) are the roots of \(f\),
    and \(\beta_j\) are the roots of \(g\).
\end{definition}
\begin{lemma}\label{lem:resultant-zero}
    \(\mathcal{R}(f,g) = 0\) if and only if \(f\) and \(g\) share a root.
\end{lemma}
\begin{proof}
    If they share a root then one of the terms in the product is 0.
\end{proof}
\begin{corollary}
    \(f\) is inseparable if and only if \(\mathcal{R}(f,f') = 0\).
\end{corollary}
\begin{proof}
    \(f\) and \(f'\) sharing a root is equivalent to
    the resultant being zero by the \hyperref[lem:resultant-zero]{lemma above}.
    Then apply Proposition~\ref{prop:derivative-inseparability}.
\end{proof}
\begin{remark}
    Notice that the resultant is closely related to the Vandermonde determinant.
    \begin{equation*}
        \mathcal{R}(f,g) = \det
        \begin{bmatrix}
            a_0 & a_1 & \cdots & a_n \\
            & a_0 & a_1 & \cdots & a_n \\
            & & \ddots & & & \ddots \\
            & & & a_0 & a_1 & \cdots & a_n \\
            b_0 & b_1 & \cdots & b_m \\
            & b_0 & b_1 & \cdots & b_m \\
            & & \ddots & & & \ddots \\
            & & & b_0 & b_1 & \cdots & b_m
        \end{bmatrix}
    \end{equation*}
    where you have \(m\) rows of \(a_i\) and \(n\) rows of \(b_i\),
    resulting in a \((m+n)\times(m+n)\) matrix.
\end{remark}

\begin{proposition}\label{prop:resultant-eval}
    Suppose \(f(x) = \sum_{i=0}^n a_i x^{n-i}\) and \(g(x) = \sum_{j=0}^m b_j x^{m-j}\).
    If \(f\) has roots \({\{\alpha_i\}}_{i=1}^n\)
    and \(g\) has roots \({\{\beta_j\}}_{j=1}^m\), then
    \begin{equation*}
        \mca{R}_{m,n}(f,g) = a_0^m \prod_{i=1}^n g(\alpha_i)
        = {(-1)}^{mn} b_0^n \prod_{j=1}^m f(\beta_j)
    \end{equation*}
\end{proposition}
\begin{proof}
    First assume \(\deg f = n\) and \(\deg g = m\).
    The base case of \(n = m = 0\) is obvious and there is nothing to prove.
    Let us proceed by way of strong induction,
    and assume this formula holds for all values smaller than \(n+m\).
    Observe from the Vandermonde determinant
    that we are simply performing row operations,
    so we have \(\mca{R}(f,g) = \mca{R}(f,r) = a_0^m \prod_{i=1}^n r(\alpha_i)\)
    as desired,
    treating \(r\) as a \(m\)-degree polynomial.
\end{proof}
\begin{remark}
    Note that the first part of the formula works when \(\deg g \leq m\),
    and similarly, the second part of the formula works when \(\deg f \leq n\).
\end{remark}

\begin{definition}
    Suppose \(f(x) \in F[x]\) is a polynomial.
    The discriminant is
    \begin{equation*}
        \mathcal{D}(f) = a_0^{2n-2} {(-1)}^{n(n-1)/2}
        \prod_{i \neq j} (\alpha_i - \alpha_j)
        = a_0^{2n-2} \prod_{i<j} {(\alpha_i - \alpha_j)}^2
    \end{equation*}
    where \(\alpha_i\) are roots.
\end{definition}
\begin{proposition}
    \(\mathcal{R}(f,f') = {(-1)}^{n(n-1)/2} a_0^{-1} \mathcal{D}(f)\).
\end{proposition}
\begin{proof}
    In some splitting field of \(f\),
    suppose we have the roots \({\{\alpha_i\}}_{i=1}^n\).
    Then we have \(f(x) = a_0 \prod_{i=1}^n (x-\alpha_i)\),
    and thus \(f'(x) = a_0 \sum_{i=1}^n \prod_{j \neq i} (x-\alpha_j)\)
    by the product rule.
    Hence \(f'(\alpha_i) = a_0 \prod_{j \neq i} (\alpha_j - \alpha_i)\),
    since all other terms disappear due to some \(\alpha_i - \alpha_i\) inside.
    By Proposition~\ref{prop:resultant-eval},
    \begin{equation*}
        \mca{R}(f,f') = a_0^{n-1} \prod_{i=1}^n f'(\alpha_i)
        = a_0^{n+(n-1)} \prod_{i=1}^n \prod_{j \neq i} (\alpha_j - \alpha_i)
        = a_0^{2n-1} \prod_{j \neq i} (\alpha_j - \alpha_i)
        = a_0^{-1} {(-1)}^{n(n-1)/2} \mca{D}(f)
    \end{equation*}
\end{proof}

\begin{proposition}
    The discriminant is invariant under translation.
\end{proposition}
\begin{proof}
    Since the discriminant is defined in terms of the difference between roots,
    if all roots are translated by the same amount,
    the differences remain the same.
\end{proof}

\subsection*{Separable Extensions}

\begin{definition}
    Suppose \(F\) is a field, and \(a\) algebraic over \(F\).
    \(a\) is a separable element if \(\min_F(a)\) is separable.
\end{definition}
\begin{definition}
    Suppose \(E/F\) is an algebraic extension.
    \(E/F\) is a separable extension if every \(a \in E\) is separable.
\end{definition}

\begin{lemma}
    Let \(f(x) = \min_F(a) \in F[x]\).
    \(f(x)\) is separable if and only if \((f,f') = 1\) are coprime.
\end{lemma}
\begin{proof}
    Let \(f(x)\) is separable.
    By way of contradiction,
    suppose \(g(x) \in F[x]\) is a monic irreducible polynomial of degree \(d\),
    where \(g \mid f\) and \(g \mid f'\).
    Let us write \(f(x) = g(x)h(x)\)
    Without loss of generality we may assume \((g,h) = 1\) are also coprime,
    since if they share factors, then send all those factors to \(g\),
    and that does not change irreducibility.
    But then \(f'(x) = g'(x)h(x) + h'(x)g(x)\),
    which implies that \(g(x) \mid g'(x)\)
    since \(g \mid h'g\), \(g \mid g'h\), and \(g \nmid h\).
    But that is not possible, since \(g'\) must have a lower degree that \(g\).
    Hence \((f,f') = 1\) are coprime.

    Now suppose \((f,f') = 1\).
    Notice they cannot share a root in the splitting field in this case,
    which by Proposition~\ref{prop:derivative-inseparability}
    means \(f(x)\) is separable.
\end{proof}

\begin{definition}
    Suppose \(E/F\) is an extension,
    and \(\func{\sigma}{F}{L}\) an embedding of fields.
    We denote the set of all homomorphisms \(\func{\sigma^\ast}{E}{L}\)
    extending \(\sigma\), that is, \(\sigma^\ast\vert_F = \sigma\) as
    \(S_\sigma = \{\sigma^\ast\in\Hom(E,L) : \sigma^\ast\vert_F = \sigma\}\).
\end{definition}
\begin{theorem}\label{thm:simple-extension-hom-count}
    Suppose \(E = F(\alpha)\) is an algebraic extension of \(F\),
    \(L = \overline{L}\) is an algebraically closed field extension of \(F\),
    % \(E = F(\alpha)\) is an algebraic extension of \(F\),
    and \(p(x) = \min_F(\alpha) \in F[x]\) is the minimal polynomial.
    If \(\func{\sigma}{F}{L}\) is an embedding,
    % that is, \(\sigma\vert_F = \id\).
    then \(\abs{S_\sigma}\),
    the number of embeddings of \(E\) into \(L\) extending \(\sigma\)
    is the number of distinct roots of \(\sigma(p)(x)\).
    In particular, \(\abs{S_\sigma} = [E:F]\)
    if and only if \(E/F\) is separable.
\end{theorem}
\begin{proof}
    % TODO: separability 1
\end{proof}

\begin{proposition}\label{prop:algebraic-extension-hom}
    Suppose \(E/F\) is an algebraic extension,
    \(L = \overline{L}\) algebraically closed,
    and \(\func{\sigma}{F}{L}\) an embedding of fields,
    Then there exists an embedding \(\func{\tau}{E}{L}\) that extends \(\sigma\),
    i.e.\ \(\tau\vert_F = \sigma\).
    If \(E\) is an algebraic closure of \(F\),
    and \(L\) is the algebraic closure of \(\sigma(F)\),
    then \(\tau\) is an isomorphism.
\end{proposition}
\begin{proof}
    % TODO: separability 1
\end{proof}
\begin{proposition}\label{prop:algebraic-extension-hom-count-bound}
    Suppose \(E/F\) is a finite extension,
    \(L = \overline{L}\) is algebraically closed,
    and \(\func{\sigma}{F}{L}\) an embedding of fields.
    % If \(E/F\) is a finite extension,
    There are at most \([E:F]\) different embeddings extending \(\sigma\),
    % extending \(\func{\sigma}{F}{L}\),
    % for \(L = \overline{L}\) algebraically closed.
    % That is, if \(S_\sigma = \{\sigma^\ast\in\Hom(E,L) : \sigma^\ast\vert_F = \sigma\}\),
    that is, \(\abs{S_\sigma} \leq [E:F]\).
\end{proposition}
\begin{proof}
    % TODO: separability 2
\end{proof}
\begin{proposition}\label{prop:intermediate-field-separable}
    Suppose \(F \subseteq E \subseteq L\) is a tower of field extensions.
    If \(L/F\) is separable, then \(L/E\) and \(E/F\) are separable.
\end{proposition}
\begin{proof}
    % TODO: separability 2
\end{proof}
\begin{theorem}\label{thm:algebraic-extension-hom-count}
    Suppose \(E/F\) is a finite extension,
    \(L = \overline{L}\) algebraically closed,
    and \(\func{\sigma}{F}{L}\) an embedding of fields.
    Then \(\abs{S_\sigma}\),
    the number of distinct embeddings of \(E\) into \(L\) extending \(\sigma\)
    is exactly \([E:F]\) if and only if \(E/F\) is separable.
\end{theorem}
\begin{proof}
    % TODO: separability 2
\end{proof}

\begin{theorem}[Transitivity of Separable Extensions]\label{thm:separable-transitive}
    Suppose \(F \subseteq E \subseteq L\) is a tower of field extensions.
    If \(E/F\) and \(L/E\) are both separable,
    then \(L/F\) is separable.
\end{theorem}
\begin{proof}
    % TODO: separability 2
\end{proof}

\subsection*{Separable Degree}

\begin{definition}
    Suppose \(E/F\) is a finite extension,
    \(L = \overline{L}\) algebraically closed,
    and \(\func{\sigma}{F}{L}\) an embedding of fields.
    We call the number of embeddings of \(E\) to \(L\) extending \(\sigma\)
    the separable degree of \(E/F\),
    denoted \({[E:F]}_s = \abs{S_\sigma}\).
\end{definition}
\begin{corollary}
    Suppose \(E/F\) is a finite extension.
    Then \({[E:F]}_s \leq [E:F]\).
\end{corollary}
\begin{proof}
    Restatement of Proposition~\ref{thm:algebraic-extension-hom-count}.
\end{proof}

\begin{definition}
    Suppose \(E/F\) an extension.
    The separable closure of \(F\) in \(E\) is \(F_s\),
    the field of all elements in \(E\) that are separable over \(F\).
\end{definition}
\begin{proposition}\label{prop:separable-degree}
    Suppose \(E/F\) an extension.
    The separable degree is \([F_s:F] = {[E:F]}_s\).
\end{proposition}
\begin{proof}
    % TODO: inseparability
\end{proof}
\begin{corollary}
    Suppose \(E/F\) a finite extension.
    Then \({[E:F]}_s \mid [E:F]\).
\end{corollary}
\begin{proof}
    Since \(F \subseteq F_s \subseteq E\) a tower of field extensions,
    \([E:F] = [E:F_s][F_s:F]\) by Theorem~\ref{thm:finite-extension-stack}.
    By \hyperref[prop:separable-degree]{proposition above}
    \([F_s:F] = {[E:F]}_s\), which divides \([E:F]\).
\end{proof}

\begin{definition}
    Suppose \(E/F\) a finite extension,
    and \(F_s\) the separable closure.
    Then the degree of inseparability is \({[E:F]}_{pi} = [E:F_s]\).
    Hence by definition \([E:F] = {[E:F]}_{pi}{[E:F]}_s\).
\end{definition}
\begin{proposition}
    Suppose \(F \subseteq L \subseteq E\) is a tower of finite extensions.
    Then \({[E:F]}_{pi} = {[E:L]}_{pi}{[L:F]}_{pi}\)
    and \({[E:F]}_s = {[E:L]}_s{[L:F]}_s\).
\end{proposition}
\begin{proof}
    % TODO: inseparability
\end{proof}

\subsection*{Simple Extensions}

\begin{definition}
    Suppose \(E/F\) is an extension.
    \(E/F\) is simple (algebraic)
    if \(E = F(\alpha)\) (for \(\alpha\) algebraic over \(F\)).
    We call \(\alpha\) a primitive element of \(E/F\).
\end{definition}
\begin{theorem}[Primitive Element Theorem]\label{thm:primitive-element}
    Suppose \(E/F\) is a finite separable extension.
    Then \(E/F\) is simple.
\end{theorem}
\begin{proof}
    % TODO: wikipedia
\end{proof}


\section{Inseparability}

\begin{remark}
    Recall from Theorem~\ref{thm:field-unique-prime-char}
    that fields come in 2 flavours,
    either characteristic 0 or prime \(p\).
\end{remark}

\begin{proposition}\label{prop:finite-extension-finite-field}
    Let \(F = \bF_p\).
    Suppose \(E/F\) is a finite extension where \([E:F] = n\).
    Then \(\abs{E} = p^n\).
\end{proposition}
\begin{proof}
    Conclusion is obvious when we view \(E\) as an \(F\)-space.
\end{proof}

\begin{definition}
    Suppose \(F\) is a field with characteristic \(p\).
    The Frobenius homomorphism is the map \(\vfunc{\Phi}{F}{F}{x}{x^p}\).
\end{definition}
\begin{proposition}\label{prop:frobenius-hom}
    The Frobenius homomorphism is an endomorphism,
    and is an automorphism if the field is finite.
\end{proposition}
\begin{proof}
    \begin{gather*}
        \Phi(x+y) = {(x+y)}^p = x^p + y^p = \Phi(x) + \Phi(y)
        \Phi(xy) = {(xy)}^p = x^p y^p = \Phi(x)\Phi(y)
    \end{gather*}
    This proves endomorphism.
    But field homomorphisms are always injective
    by Theorem~\ref{thm:field-hom-injective},
    and so by the \hyperref[thm:pigeonhole]{pigeonhole principle}
    it is also surjective,
    which proves automorphism.
\end{proof}
\begin{corollary}
    Any nonzero element \(a \in \bF_p^\star\) is a \(p\)th power.
\end{corollary}
\begin{proof}
    Simple restatement of the \hyperref[prop:frobenius-hom]{proposition above}.
\end{proof}

\begin{proposition}\label{prop:separable-power-polynomial}
    Suppose \(F\) is a field of characteristic \(p\),
    and \(f(x) \in F[x]\) an irreducible polynomial.
    Then there exists some \(g(x) \in F[x]\) irreducible and separable
    such that \(f(x) = g(x^{p^m})\) for some unique \(m \geq 0\).
\end{proposition}
\begin{proof}
    % TODO: inseparability
\end{proof}
\begin{definition}
    We call the degree of \(g\) the inseparable degree of \(f(x)\),
    and \(p^m\) the separable degree of \(f(x)\).
\end{definition}
\begin{proposition}
    Suppose \(E = F(\alpha)\) is an extension of \(F\),
    and \(f(x) = \min_F(\alpha)\).
    Then the definitions of separable and inseparable degrees
    for the polynomial and the field coincide,
    that is, \({[E:F]}_s\) is the separable degree of \(f(x)\),
    and \({[E:F]}_{pi}\) is the inseparable degree of \(f(x)\).
\end{proposition}
\begin{proof}
    % TODO: inseparable
\end{proof}

\begin{proposition}
    Suppose \(F\) is a field.
    Then all roots of \(f(x)\) have the same multiplicity.
    In particular,
    \begin{enumerate}[label={(\alph*)}, itemsep=0mm]
        \item if \(F\) has characteristic 0, the multiplicity is 1; and
        \item if \(F\) has characteristic \(p\),
            the multiplicity is \(p^n\) for some \(n \in \bN\)
    \end{enumerate}
\end{proposition}
\begin{proof}
    If \(F\) has characteristic 0,
    we know that the only irreducible polynomials are linear ones.
    They clearly have one root of multiplicity 1.

    Now consider the case of characteristic \(p\).
    Let \(\{\alpha,\beta\}\subset\overline{F}\) be roots of \(f(x)\).
    Consider the extensions \(F(\alpha)\) and \(F(\beta)\),
    and the homomorphism \(\vfunc{\sigma}{F(\alpha)}{F(\beta)}{\alpha}{\beta}\)
    where \(\sigma\vert_F = \id\).
    By Proposition~\ref{prop:algebraic-extension-hom},
    we can extend \(\sigma\) to \(\tau\in\Aut(\overline{F})\).
    Let \(f(x) = {(x-\alpha)}^m h(x) \in \overline{F}[x]\), \(h(\alpha) \neq 0\).
    Then \(f(x) = \tau(f)(x) = {(x-\beta)}^m \tau(h)(x)\).
    Therefore multiplicity of \(\alpha\) at most the multiplicity of \(\beta\).
    But this argument is symmetric,
    so the multiplicity of \(\alpha\) is also at least multiplicity of \(\beta\).
    Hence the multiplicities are equal.

    Now suppose \(f(x)\) irreducible.
    Note that from Proposition~\ref{prop:separable-power-polynomial}
    we can find \(g(x) \in F[x]\) such that \(f(x) = g(x^{p^m})\).
    If \(a\) is a root of \(f(x)\), then \(a^{p^m}\) is a root of \(g(x)\),
    and hence \(a\) has multiplicity \(p^m\)
    since \(x^{p^m} - a^{p^m} = {(x-a)}^{p^m}\).
\end{proof}

\begin{definition}
    Suppose \(F\) is a field with characteristic \(p\),
    and \(E/F\) an algebraic extension.
    An element \(\alpha \in E\) is purely inseparable
    if \(\min_F(\alpha)\) has only one distinct root.
    % if there exists some \(k \geq 1\) such that \(a^{p^k} \in F\).
\end{definition}
\begin{definition}
    Suppose \(E/F\) an algebraic extension.
    \(E/F\) is purely inseparable
    if all elements in \(E\) are purely inseparable over \(F\).
\end{definition}
\begin{lemma}\label{lem:purely-inseparable-power}
    Suppose \(F\) is a field with characteristic \(p\).
    If \(\alpha\) is algebraic over \(F\),
    then \(\alpha\) is purely inseparable over \(F\)
    if and only if \(\alpha^{p^n} \in F\) for some \(n\).
    In this case, \(\min_F(\alpha) = {(x-\alpha)}^{p^n}\).
\end{lemma}
\begin{proof}
    % TODO: inseparable
\end{proof}

\begin{theorem}
    Suppose \(K/F\) is an algebraic extension.
    If \(\alpha \in K\) is both separable and purely inseparable,
    then \(\alpha = F\).
\end{theorem}
\begin{proof}
    % TODO: inseparable
\end{proof}
\begin{theorem}
    If \(K/F\) is purely inseparable, then \(K/F\) is normal.
    If \(K/F\) is purely inseparable, finite, and \(F\) has characteristic \(p\),
    then \([K:F] = p^n\) for some \(n\).
\end{theorem}
\begin{proof}
    % TODO
\end{proof}
\begin{theorem}
    Suppose \(X\) a set, and \(K = F(X)\),
    with alll \(\alpha \in X\) purely inseparable.
    Then \(K\) is purely inseparable.
\end{theorem}
\begin{proof}
    % TODO
\end{proof}
\begin{theorem}
    Suppose \(F \subseteq L \subseteq K\) are a tower of extensions.
    \(K/F\) is purely inseparable if and only if
    \(K/L\) and \(L/F\) are purely inseparable.
\end{theorem}
\begin{proof}
    % TODO
\end{proof}

% TODO: separable and inseparable closures


\section{Perfect Fields and Normal Extensions}

\subsection*{Perfect Fields}

\begin{definition}
    Suppose \(F\) is a field.
    \(F\) is perfect if every algebraic extension of \(F\) is separable.
\end{definition}
\begin{proposition}
    Suppose \(F\) is a field with characteristic \(p\).
    \(F\) is perfect if and only if \(F^p = F\),
    i.e.\ the Frobenius endomorphism \(\vfunc{\Phi_p}{F}{F}{x}{x^p}\) is bijective.
\end{proposition}
\begin{proof}
    % TODO
\end{proof}

\begin{proposition}
    Algebraically closed fields are perfect.
\end{proposition}
\begin{proof}
    % TODO
\end{proof}
\begin{theorem}
    Finite fields are perfect.
\end{theorem}
\begin{proof}
    % TODO
\end{proof}

\begin{lemma}
    Suppose \(F\) is a field with characteristic \(p\).
    If \(a \in F - F^p\), then \(x^p - a\) is irreducible and inseparable.
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{lemma}
    Suppose \(F\) is a field with characteristic \(p\).
    If \(a \in F^p\), then \(x^p - a\) is reducible.
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{proposition}
    Suppose \(p\) is a prime,
    and \(x^p - 1\) splits completely over a field \(K\).
    Let \(L/K\) be an extension, with \(a \in L\) an algebraic element over \(K\),
    and the prime \(p \nmid [K(a):K]\) does not divide the degree of the extension.
    Then \(K(a) = K(a^p)\).
\end{proposition}
\begin{proof}
    % TODO
\end{proof}
\begin{theorem}
    A field \(K\) is perfect
    if and only if its characteristic is 0,
    or if its characteristic is \(p\) and \(K^p = K\).
\end{theorem}
\begin{proof}
    % TODO
\end{proof}

\subsection*{Normal Extensions}

\begin{definition}
    Suppose \(K/F\) is an algebraic extension.
    \(K/F\) is normal if \(f(x) \in F[x]\) irreducible over \(F\)
    and has a root in \(K\) implies \(f(x)\) splits completely in \(K\).
\end{definition}
\begin{remark}
    In general, normality is not a transitive property,
    meaning that it does not stack.
\end{remark}

\begin{theorem}
    Suppose \(F \subseteq K \subseteq L\) is a tower of extensions.
    If \(L/F\) is normal, then \(L/K\) is normal.
\end{theorem}
\begin{proof}
    % TODO
\end{proof}

\begin{lemma}
    Suppose \(F \subseteq E_i \subseteq E\) are two towers of extensions with \(i \in \{1,2\}\).
    If \(E_1/F\) and \(E_2/F\) are normal,
    then \((E_1 \cdot E_2)/F\) and \((E_1 \cap E_2)/F\) are normal.
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{lemma}
    Suppose \(F\) is a field, and \(K/F\) is an algebraic extension.
    Let \(I\) be some index set, and \(i \in I\),
    with \(F \subseteq E_i \subseteq K\) are intermediate extensions
    such that \(E_i/F\) is normal.
    Then \(\bigcap_{i \in I} E_i\) is a normal extension of \(F\).
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{lemma}
    Suppose \(K/F\) is a normal extension,
    and \(K_\text{sep}\) denotes the separable closure of \(F\) in \(K\).
    Then \(F \subseteq K_\text{sep} \subseteq K\) is a tower of normal extensions.
\end{lemma}
\begin{proof}
    % TODO
\end{proof}

\begin{proposition}
    Let \(F \subseteq K \subseteq L\) be a tower of field extensions.
    \begin{enumerate}[label={(\alph*)}, itemsep=0mm]
        \item If \(K/F\) is normal, and \(\tau \in \Aut_F(L)\) is an \(F\)-automorphism,
            then \(\tau\vert_K \in \Aut_F(K)\).
        \item If \(L/F\) is normal, then any \(\sigma \in \Hom_F(K,L)\)
            extends to and \(F\)-automorphism over \(L\).
    \end{enumerate}
\end{proposition}
\begin{proof}
    % TODO
\end{proof}

\begin{theorem}\label{thm:normal-extension-equivalence}
    Suppose \(E/F\) is an algebraic extension, with \(E \subseteq \overline{F}\).
    The following are equivalent:
    \begin{enumerate}[label={(\alph*)}, itemsep=0mm]
        \item Every \(\sigma\in\Hom_F(E,\overline{F})\) is also \(\sigma\in\Aut_F(E)\);
        \item \(E\) is a splitting field of a family of polynomials in \(F[x]\); and
        \item \(E/F\) is normal.
    \end{enumerate}
\end{theorem}
\begin{proof}
    % TODO
\end{proof}


\section{Finite Fields}

\begin{proposition}[Existence of Finite Fields]\label{prop:existence-finite-fields}
    Any finite field must be of order \(p^n\) for some prime \(p\),
    and such fields exists for all \(n \in \bN\).
\end{proposition}
\begin{proof}
    Suppose \(F\) is a finite field of characteristic \(p\).
    Treating \(F\) as an additive group, \(1 \in F\), \(p \mid \abs{F}\).
    Suppose, by way of contradiction,
    that there exists another prime \(q \neq p\) such that \(q \mid \abs{F}\).
    Then by \hyperref[thm:cayley]{Cauchy's theorem},
    there exists \(x \in F\) with order \(q\) so \(qx = 0\).
    By \hyperref[thm:bezout]{B\'ezout's identity},
    there exists some \(a,b\) such that \(ap + bq = 1\).
    Hence \(x = (ap+bq)x = a(px) + b(qx) = 0\),
    which is contradiction as \(0\) does not have order \(q\).

    We can then apply Proposition~\ref{prop:finite-extension-finite-field}
    and simply have \(\bF_p(x)\), with \(x^n \in 1\) to be our finite field.
\end{proof}

\begin{lemma}\label{lem:finite-mult-group-cyclic}
    Suppose \(K\) is a field,
    and \(G \subseteq K^\ast\) a finite subgroup of the multiplicative group.
    Then \(G\) is cyclic.
\end{lemma}
\begin{proof}
    Let \(\abs{G} = n\), and \(m = \exp(G)\).
    By \hyperref[cor:order-element-group]{Lagrange's theorem}, \(m \mid n\).
    If \(g \in G\), then \(g^m = 1\), so each element of \(G\) is a root of \(x^m - 1\).
    This polynomial has at most \(m\) roots on \(K\),
    which implies all the elements of \(G\) are roots of \(x^m - 1\), so \(n \leq m\).
    Hence we have \(\exp(G) = \abs{G}\) so \(G\) is cyclic.
\end{proof}
\begin{corollary}
    If \(K/F\) is an extension of finite fields,
    then \(K\) is a simple extension of \(F\).
\end{corollary}
\begin{proof}
    Consider \(\abs{K} = p^n\), so \(\abs{K^\ast} = p^n - 1\).
    If \(a \in K^\ast\), then \(a^{p^{n-1}} = 1\).
    Hence \(a^{p^n} = a\) for all \(a \in K\).
    \(K\) is then the splitting field of \(x^{p^n}-x\) over \(\bF_p\),
    and is normal over \(\bF_p\) by Theorem~\ref{thm:normal-extension-equivalence}.
    The \hyperref[prop:derivative-inseparability]{derivative test} yields separability.

    Conlcude from the \hyperref[thm:primitive-element]{primitive element theorem}
    and the \hyperref[lem:finite-mult-group-cyclic]{lemma above},
    since cyclic groups have a single generator.
\end{proof}
\begin{remark}
    In fact the primitive element
    does not have to be a generator of the multiplicative group.
\end{remark}
\begin{corollary}[Uniqueness of Finite Fields]\label{cor:uniqueness-finite-field}
    Finite fields of the same cardinality are unique up to isomorphism.
\end{corollary}
\begin{proof}
    Any two fields of order \(p^n\) are splitting fields over \(\bF_p\) of \(x^{p^n} - x\).
    Conclude by \hyperref[thm:uniqueness-splitting-field]{uniqueness of splitting fields}.
\end{proof}

\begin{lemma}\label{lem:finite-field-quotient}
    The finite field \(\bF_{p^n}\) is expressible as \(\bF_p[x]/(f)\)
    for some \(f(x) \in \bF_p[x]\) of degree \(n\).
\end{lemma}
\begin{proof}
    Since Lemma~\ref{lem:finite-mult-group-cyclic}
    tells us that \(\bF_{p^n}^\ast\) is cyclic,
    we pick \(\theta \in \bF_{p^n}\) to generate it.
    Hence \(\theta\) generates \(\bF_{p^n}\) over \(\bF_p\),
    and it will satisfy some irreducible polynomial \(f \in \bF_p[x]\).
    Then the evaluation map \(\vfunc{\phi}{\bF_p[x]}{\bF_{p^n}}{x}{\theta}\)
    induces an isomorphism \(\bF_p[x]/(f) \cong \bF_{p^n}\),
    since \(\deg f = n\).
\end{proof}
\begin{corollary}
    Suppose \(F\) is a finite field,
    and \(f(x) \in F[x]\) is a monic irreducible polynomial of degree \(n\).
    Then if \(a\) is a root of \(f\) in an extension of \(F\),
    then \(F(a)\) is the splitting field of \(f\).
    Consequently, if \(K\) is a splitting field of \(f\),
    then \([K:F] = n\).
    If \(\abs{F} = q\), then the roots are \(a^{q^r}\) for \(r \geq 1\).
\end{corollary}
\begin{proof}
    Let \(K\) be a splitting field of \(f\).
    If \(a \in K\) is a root,
    then \(F(a)\) is an extension of \(F\) of degree \(n\).
    By irreducibility \(f(x) = \min_F(a)\),
    and the minimal polynomial splits in \(F(a)\).
    Hence \(K = F(a)\) is degree \(n\).

    Lastly, we see that \(\min_F(a) = {(x-a)}^{p^n}\)
    by Lemma~\ref{lem:purely-inseparable-power},
    and clearly \(a^q - a = 0\).
\end{proof}

\begin{proposition}
    For some prime \(p\) and \(n,m \in \bN\),
    \(m \mid n \iff \bF_{p^m} \subseteq \bF_{p^n}\).
\end{proposition}
\begin{proof}
    \(\bF_{p^m}\) is the set of roots of \(x^{p^m} - x\)
    by the \hyperref[cor:uniqueness-finite-field]{uniqueness of finite fields}
    in some algebraic closure \(\overline{\bF}_p\).
    Note that if \(m \mid n\), then \(n = dm\), so
    \begin{equation*}
        x^{p^n} = x^{p^{dm}} = {(x^{p^{(d-1)m}})}^{p^m} = x^{p^{(d-1)m}}
        = \cdots = x^{p^m} = x
    \end{equation*}
    so \(x\) is a root of \(x^{p^n} - x\), and \(x \in \bF_{p^n}\).

    Conversely, suppose \(\bF_{p^m} \subseteq \bF_{p^n}\).
    Then \(\bF_{p^n}\) can be treated as a \(\bF_{p^m}\)-vector space of dimension \(d\),
    by Proposition~\ref{prop:field-extension-vsp}.
    Hence \(p^n = \abs{\bF_{p^n}} = \abs{\bF_{p^m}}^d = {(p^m)}^d = p^{md}\),
    and \(m \mid n\).
\end{proof}

\begin{proposition}
    Let \(n \in \bN\).
    Then \(x^{p^n} - x\) factors over \(\bF_p\)
    into the product of all monic irreducible polynomials over \(\bF_p\)
    of degree \(m\), where \(m \mid n\).
\end{proposition}
\begin{proof}
    % TODO: finite fields
\end{proof}

\begin{lemma}
    Let \(f \in \bF_q[x]\) be an irreducible polynomial over some finite field \(\bF_q\),
    and let \(\alpha\) be a root of \(f\) in some extension.
    Then, for a polynomial \(h \in \bF_q[x]\),
    \(h(\alpha) = 0\) if and only if \(f \mid h\).
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{lemma}
    Let \(f \in \bF_q[x]\) be an irreducible polynomial of degree \(m\).
    Then \(f \mid x^{q^n} - x\) if and only if \(m \mid n\).
\end{lemma}
\begin{proof}
    % TODO
\end{proof}
\begin{corollary}
    If \(N_q(d)\) is the number of monic irreducible polynomials
    in \(\bF_q[x]\) of degree \(d\), then
    \begin{equation*}
        q^n = \sum_{d \mid n} d N_q(d) \qquad \forall n \in \bN
    \end{equation*}
    where we are summing over all positive \(d \mid n\).
\end{corollary}
\begin{proof}
    % TODO
\end{proof}
